---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%",
  fig.align = "center"
)
library(PandemicSim)
```

# {PandemicSim}: Simulate pandemics

With this package you can simulate a pandemic for a population of dots living in a small box.
You have a lot of options to change the pandemic.
For example you can change the number of individuals or increase the population's mobility. You can also make the disease more infectious or more deadly and you can change how fast individuals recover. You can even simulate the effect of countermeasures.

## Installation

```{r, eval = FALSE}
devtools::install_github("janoleko/PandemicSim")
```

## Example

First simulate the pandemic (in this case with default settings, but you could change them)
```{r, results = 'hide'}
pandemic = sim_pandemic()
```
Then plot the result
```{r}
plot_pandemic(pandemic, t = 100)
plot_pandemic(pandemic, t = 200)
plot_pandemic(pandemic, t = 300)
```
